Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations

### 2021-11-20 analysis/paper/paper.Rmd
added Nick's gastric lavage code

```{r load-libraries}
library(tidyverse)
library(magrittr)
library(lubridate)
library(tidytable)
library(janitor)
library(purrr)
library(here)
library(FSA)
library(knitr)
library(kableExtra)

@@

>>>>

```{r load-libraries}
library(tidyverse)
library(magrittr)
library(lubridate)
library(tidytable)
library(janitor)
library(purrr)
library(here)
library(FSA)
library(knitr)
library(kableExtra)
library(stringi)

@@

```{r gastric-data}
gastric_df = raw_df %>%
  filter(species == "Northern Pikeminnow") %>%
  mutate(fish_or_parts = case_when(stri_detect_fixed(stomach_contents, "Fish") ~ "Fish or Fish Parts",
                                   stri_detect_fixed(stomach_contents, "Empty") ~"Empty",
                                   stri_detect_fixed(comments, "Whole scuplin") ~ "Fish or Fish Parts",
                                   stri_detect_fixed(stomach_contents, "Whitefish") ~ "Fish or Fish Parts",
                                   TRUE ~ "Other")) %>%
  drop_na(length) %>%
  mutate(non_fish_wt = stomach_contents_weight - fish_content_weight) %>%
  dplyr::select(date, length, lavage_id, stomach_contents, comments, fish_or_parts, stomach_contents_weight, non_fish_wt,                  fish_content_weight) %>%
  filter(!stomach_contents %in% c("Lost sample CG27-001", "Did Not Lavage")) %>%
  drop_na(stomach_contents)
